The Early Eocene Climate Optimum reconstructed with Bayesian multi-proxy integration

### 2022-08-16 manuscript/manuscript.Rmd
manuscript update

---
title: "The Early Eocene Climate Optimum reconstructed with Bayesian multi-proxy integration"
author:
  - Kilian Eichenseer^[Department of Earth Sciences, Durham University, South Road, DH1 3LE, Durham, United Kingdom] and Lewis A. Jones^[Centro de Investigación Mariña, Grupo de Ecoloxía Animal, Universidade de Vigo, 36310 Vigo, Spain]
output:
  word_document:
    reference_docx: "template.docx"
bibliography: references.bib
csl: palaeontology.csl
---

@@

# Introduction

Contrast between complex, process-driven Earth system models and very simplistic use of the proxy data as local temperature estimates or global averages. Here, we introduce a proxy-driven modelling approach of relatively low complexity, which places the available chemical and biological proxy data in a single climate model.
In order to properly compare model output to proxy data, latitudinal temperature patterns need to be reconstructed from noisy data (impossible to properly compare model gradients with scattered proxy points "by eye")

@@

# Materials & Methods

>>>>

---
title: "The Early Eocene Climate Optimum reconstructed with Bayesian multi-proxy integration"
"Improving palaeoclimatic reconstructions with ecological data: How hot was the early Eocene?"
"Integrating ecological and geochemical proxies for palaeoclimatic reconstruction: An early Eocene example"

author:
  - Kilian Eichenseer^[Department of Earth Sciences, Durham University, South Road, DH1 3LE, Durham, United Kingdom] and Lewis A. Jones^[Centro de Investigación Mariña, Grupo de Ecoloxía Animal, Universidade de Vigo, 36310 Vigo, Spain]
output:
  word_document:
    reference_docx: "template.docx"
bibliography: references.bib
csl: palaeontology.csl
---

@@

# Introduction
The geological record holds evidence for episodes in Earth history with fundamentally different climates than our current. Some episodes, for example the early Eocene, are thought to have been significantly warmer than the modern, potentially representing an analogue for extreme climate warming scenarios. Reconstructions of palaeoclimate commonly follow one of two approaches. Geochemical proxies such as oxygen isotopes (d18O), tetraether indices (TEX86) and magnesium calcium ratios (Mg/Ca) are used to derive palaeotemperature estimates for individual locations using experimentally derived transfer functions. Multiple local estimates are sometimes summarised to generate regional or global estimates, but this approach is prone to sampling bias [@Jones2022]. Earth system models take a fundamentally different approach by modelling the climate-generating processes directly, reconstructing spatially resolved climate estimates for the entire glob.e This approach is, however, relying on proxy data to constrain the large number of possible model setups and ground truth the model output.

@@

<!--

Contrast between complex, process-driven Earth system models and very simplistic use of the proxy data as local temperature estimates or global averages. Here, we introduce a proxy-driven modelling approach of relatively low complexity, which places the available chemical and biological proxy data in a single climate model.
In order to properly compare model output to proxy data, latitudinal temperature patterns need to be reconstructed from noisy data (impossible to properly compare model gradients with scattered proxy points "by eye")
-->
# Materials & Methods
